---
title: "textmining"
author: "Gemei"
output:
  word_document: default
  pdf_document:
    latex_engine: xelatex
---

```{r package}
library(tidyverse)
library(tidytext)
library(janeaustenr)
library(stringr)
library(gutenbergr)
library(scales)
```
##1.	Pick three authors from Gutenberg.org and download their works.  Compare the authors.  Which two are more alike?  Some suggestions:  Mark Twain, Leo Tolstoy, Charles Dickens.
```{r}
Twain <- gutenberg_download(c(76,74,3179))
Tolstoy <- gutenberg_download(c(1399,2142,2637))
Dickens <- gutenberg_download(c(98,766,1400))

tidy_Twain <- Twain %>%
  unnest_tokens(word, text) %>%
  mutate(word = str_extract(word, "[a-z']+")) %>% #remove the font/italics
  anti_join(stop_words)
tidy_Twain %>%
  count(word, sort = TRUE)

tidy_Tolstoy <- Tolstoy %>%
  unnest_tokens(word, text) %>%
  mutate(word = str_extract(word, "[a-z']+")) %>% #remove the font/italics
  anti_join(stop_words)
tidy_Tolstoy %>%
  count(word, sort = TRUE)

tidy_Dickens <- Dickens %>%
  unnest_tokens(word, text) %>%
  mutate(word = str_extract(word, "[a-z']+")) %>% #remove the font/italics
  anti_join(stop_words)
tidy_Dickens %>%
  count(word, sort = TRUE)

#frequency
frequency_by_word_across_authors <- bind_rows(mutate(tidy_Twain, author = "Twain"),
                                              mutate(tidy_Tolstoy, author = "Tolstoy"),
                                              mutate(tidy_Dickens, author = "Dickens")) %>% mutate(word = str_extract(word, "[a-z']+")) %>% count(author, word) %>%
  group_by(author) %>%
  mutate(proportion = n / sum(n)) %>% select(-n) %>%
  spread(author, proportion)

frequency <- frequency_by_word_across_authors %>% 
  gather(author, proportion, `Tolstoy`:`Twain`)

df_Tolstoy <- frequency[frequency$author == "Tolstoy",]
cor.test(data = df_Tolstoy, ~ proportion + `Dickens`)

df_Twain <- frequency[frequency$author == "Twain",]
cor.test(data = df_Twain, ~ proportion + `Dickens`)
```
So Tolstoy and Dickens are more alike.

##Let’s look at how the sentiment changes across the length of a book by looking at 80 lines at a time.  Compare how sentiment changes in Victor Hugo’s Les Miserables and Charles Dickens’ A Tale of Two Cities.  Look at negative vs positive sentiment.  Then pick a sentiment like joy or anger or fear or …  and see how that sentiment compares. 
```{r}
Hugo <- gutenberg_download(135)
Tale <- gutenberg_download(98)
tidy_Hugo <- Hugo %>%
  unnest_tokens(word, text) %>%
  mutate(word = str_extract(word, "[a-z']+")) %>% #remove the font/italics
  anti_join(stop_words)
tidy_Hugo %>%
  count(word, sort = TRUE)

tidy_Hugo <- Hugo %>% 
  mutate(linenumber = row_number(),
         chapter = cumsum(str_detect(text,
                                     regex("^chapter [\\divxlc]",
                                           ignore_case = TRUE)))) %>%
  ungroup()%>%
  # use word so the inner_join will match with the nrc lexicon
  unnest_tokens(word, text)

Hugosentiment <- tidy_Hugo %>% 
  inner_join(get_sentiments("bing")) %>%
  count(index = linenumber %/% 80, sentiment) %>% 
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)
Hugosentiment %>%
  ggplot(aes(index, sentiment)) + 
  geom_col(show.legend = FALSE,scales = "free_x")

#a tale of two cities
tidy_Tale <- Tale %>% 
  mutate(linenumber = row_number(),
         chapter = cumsum(str_detect(text,
                                     regex("^chapter [\\divxlc]",
                                           ignore_case = TRUE)))) %>%
  ungroup()%>%
  # use word so the inner_join will match with the nrc lexicon
  unnest_tokens(word, text)
  
Talesentiment <- tidy_Tale %>% 
  inner_join(get_sentiments("bing")) %>%
  count(index = linenumber %/% 80, sentiment) %>% 
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)
Talesentiment %>%
  ggplot(aes(index, sentiment)) + 
  geom_col(show.legend = FALSE,scales = "free_x")

#specific sentiments
joy=get_sentiments("nrc")%>%filter(sentiment=="joy")

#a tale of two cities
Talesentiment <- tidy_Tale %>% 
  inner_join(joy) %>%
  count(index = linenumber %/% 80, sentiment) %>% 
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = joy)
Hugosentiment <- tidy_Hugo %>% 
  inner_join(joy) %>%
  count(index = linenumber %/% 80, sentiment) %>% 
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = joy)

ggplot(Hugosentiment,aes(index,sentiment)) +geom_col()+ggtitle("Les Miserable")
ggplot(Talesentiment,aes(index,sentiment)) +geom_col()+ggtitle("A tale of two cites")
```

We can see that both of the books used a lot of negative words than positive words,in Les Miserable, the word joy is used more towards the end of the book, where in A tale of two cities, the word is used more in the first half of the book and less in the second half of the book.
